---
title: "Comparison of different data versions"
author: "Frederik Aust"
date: "`r Sys.Date()`"

toc: true
number-sections: true
reference-location: margin

highlight-style: github
theme: lumen

execute:
  keep-md: true

format:
  html:
    code-fold: true
    standalone: true
    embed-resources: true
    self-contained: true
    link-external-icon: true
    citations-hover: true
    footnotes-hover: true
---

```{r}
#| label: init
#| include: false

library("dplyr")
library("purrr")
```

```{r}
#| label: load_data

data_version <- list.files(
  path = "./../../data"
  , pattern = "data\\d\\.rds$"
  , full.names = TRUE
)

data_version <- data_version[-which(basename(data_version) == "blinded_data4.rds")]

reppag2009_data <- lapply(data_version, readRDS)
names(reppag2009_data) <- basename(data_version)
names(reppag2009_data)
```


# Number of participants

```{r}
reppag2009_data_summary <- map(
  .x = reppag2009_data
  , .f = \(x) {
    tibble::tibble(
      # n = n_distinct(x$participant_id)
      # ids = unique(x$participant_id) |>
      #   list()
      dishonesty = summarize(
        x
        , across(matches("dishonesty_[sh]"), unique)
        , .by = participant_id
      ) |>
        rename(dishonesty = matches("dishonesty_[sh]")) |>
        list()
      , dishonesty_recalculated = {
          if(any(grepl("reward", colnames(x)))) {
            x <- filter(x, reward > 1)
          }
          summarize(
            x
            , wins = sum(correct == "win")
            , trials = n()
            , dishonesty_recalculated = wins / trials
            , .by = c(participant_id, condition)
          ) |> 
          filter(condition == "op") |>
          dplyr::select(-condition) |>
          list()
        }
    )
  }
)

reppag2009_data_summary_dishonesty <- map(
  .x = reppag2009_data_summary
  , .f = \(x) {
      bind_cols(
        arrange(x$dishonesty_recalculated[[1]], dishonesty_recalculated)
        , arrange(x$dishonesty[[1]], dishonesty) |>
          dplyr::select(-participant_id)
      )
  }
)
```

It seems participant a few participants were removed in v5 and either added back in or replaced for v7.
Some others are only added in v7 (e.g., 1050, 1054)

::: {.callout-info}
Need to check e-mails for included/excluded participants.
:::

```{r}
#| label: tbl-participant-ids
#| tbl-cap: "Participant IDs in each data version."

knitr::kable(
  map(
    reppag2009_data_summary_dishonesty
    , "participant_id"
  ) |>
    map(\(x) {
      x <- as.numeric(as.character(x))
      res <- rep(NA, 67)
      res[x - 1000] <- x
      res
    }) |>
    bind_cols()
  , format = "markdown"
)
```


# Dishonesty

Let's first check the number of trials included in each data version.
Something seems to be wrong in v5 relative to the other versions.
Differences between v1 and v7 seem to be due to different numbers of trials due to differences in handling missing responses.
For some reason a few participants have substantially fewer trials in v1 than v7 (e.g., 1002, 1037, 1047, 1049).
Although v1 and v7 seem to be pretty close in original honesty scores, there are some differences that don't seem to be due to rounding.

It's really weird that my recalculated dishonesty scores in v1 match those in v7 exactly, except where the number of trials differ!
Yet they differ from those originally in the data.


::: {.callout-info}
Need to check e-mails for selection of trials.
:::

```{r}
#| label: tbl-dishonesties
#| tbl-cap: "Dishonesty scores in each data version."

reppag2009_data_summary_dishonesty_joined <- map(
    reppag2009_data_summary_dishonesty
    , \(x) dplyr::select(
      x
      , participant_id
      , trials
      , dishonesty
      , dishonesty_recalculated
    )
  ) |>
    reduce(
      full_join
      , by = "participant_id"
      , suffix = c("1", "5")
    ) |>
    arrange(participant_id) |>
    dplyr::select(
      participant_id
      , matches("trials")
      , matches("dishonesty\\d*$")
      , everything()
    )

knitr::kable(reppag2009_data_summary_dishonesty_joined)
```

From this is seems that something went seriously wrong in v5.
This does not inspire confidence and needs to be explained!

```{r}
plot(
  dishonesty ~ dishonesty1
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)

plot(
  dishonesty1 ~ dishonesty5
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)

plot(
  dishonesty ~ dishonesty5
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)
```

```{r}
plot(
  dishonesty_recalculated1 ~ dishonesty1
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)

plot(
  dishonesty_recalculated5 ~ dishonesty5
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)

plot(
  dishonesty_recalculated ~ dishonesty
  , data = reppag2009_data_summary_dishonesty_joined
)
abline(0, 1)
```

It is also pretty weird that the dishonesty sores apparently were not shuffled.
This is fine, but was implied otherwise in the e-mail conversation?
